### 2025-11-04 Proposals/2025-NSF-EntropicGeometry/NarrativeBody.tex
Added a few more refs and changed text that needs work to blue

\noindent
\textbf{Expected outcomes and significance:}
During the three-year period of the proposed research, we expect to achieve and submit manuscripts on at least the following:
\begin{enumerate}
	\item Demonstrate that the Shannon entropy can be recovered as the maximum entropy increase under mixture for all ensemble spaces, and that the Shannon, Gibbs and von Neumann entropies can be recovered in the specific cases of discrete classical, continuous classical, and quantum mechanics
	\item Show that the geometric structures of classical and quantum mechanics can be recovered from the entropic structure alone 
	\item Demonstrate that information geometry can be generalized to the ensemble space of any physical theory of finite dimensions 
	\item Show that the entropic structure imposes constraints on the space of possible physical theories and rules out some Generalized Probabilistic Theories
\end{enumerate}
Additional possible outcomes during or subsequent to the period of proposed activities depending on the rate of advancement include \textcolor{blue}{[list near-term possible outcomes.  Then discuss possible longer-term future developments stemming from this work]}

Near-term possible: 
Find what results from information geometry and information theory could be generalized to ensemble spaces. \textcolor{blue}{Naturally lends itself to various self-contained contributions by the grad student, undergrads, or individuals outside the project}

Determine whether the convexity of the mixing entropy can be physically motivated and whether that guarantees a continuous embedding into a locally convex topological vector space.

Generalize information geometry to the infinite-dimensional case---would require a locally convex topology to be able to define variations.

Determine whether the ensemble spaces can be in general proven to be metrizable and characterize the connection between the metric and the entropy.

Generalize classical mechanics and classical field theory.

Find a suitable function space that can be used as a model for the case of classical field theories.

The primary significance of the proposed research is that it will \textcolor{blue}{[has the potential to?]} provide a common axiomatic foundation for \emph{all} physical theories.  Such an axiomatic foundation common to all physical theories will serve not only to better ground current theories and elucidate their relationships to one another, but also to constrain potential future physical theories, and perhaps point to assumptions or structures in current theories that hold promise for modification in order to develop new theories.

[We don't know where the mathematical structures in physics come from.  Therefore, when people try to generalize them, they do not know in which direction they can be generalized.  What we're doing is instead finding axioms from physical requirements---things the physics must at least give you.  The axiomatics are justified from the physics.  We're doing the due diligence to check that the axioms can be justified from the physics and they're independent of each other.  So when we're doing the generalization, the generalization is better constrained by the physics.]

Regarding the relationship of this work to the present state of knowledge in the field, while there exists other work attempting to reconstruct quantum mechanics from physical principles, for example in Refs.~\textcolor{blue}{[cite Hardy, Ariel, Pavia, see 2:36 into talk by Nicolas Medina Sanchez (Vienna) at Perimeter], we are not aware of any literature attempting to relate the geometric and entropic structures of quantum mechanics, much less in a general physical theory. One sentence about general approach(es) of those works?  There are people trying to reconstruct QM from physical premises, but these works are typically on finite dimensions and do not generalize to CM, and definitely don't generalize to classical or quantum field theories.}

@@

\noindent
\textbf{Assessment of intellectual merit:} \\
We will know if the proposed research program is successful if [proofs work!].  [Alternatively, if we conclude that these axioms are insufficient.]

>>>>

\noindent
\textbf{Expected outcomes and significance:}
During the three-year period of the proposed research, we expect to achieve and submit manuscripts on at least the following:
\begin{enumerate}
	\item Demonstrate that the Shannon entropy can be recovered as the maximum entropy increase under mixture for all ensemble spaces, and that the Shannon, Gibbs and von Neumann entropies can be recovered in the specific cases of discrete classical, continuous classical, and quantum mechanics
	\item Show that the geometric structures of classical and quantum mechanics can be recovered from the entropic structure alone 
	\item Demonstrate that information geometry can be generalized to the ensemble space of any physical theory of finite dimensions 
	\item Show that the entropic structure imposes constraints on the space of possible physical theories and rules out some Generalized Probabilistic Theories
\end{enumerate}
\textcolor{blue}{Additional possible outcomes during or subsequent to the period of proposed activities depending on the rate of advancement include [list near-term possible outcomes.  Then discuss possible longer-term future developments stemming from this work]}

\textcolor{blue}{Near-term possible: 
Find what results from information geometry and information theory could be generalized to ensemble spaces. Naturally lends itself to various self-contained contributions by the grad student, undergrads, or individuals outside the project}

\textcolor{blue}{Determine whether the convexity of the mixing entropy can be physically motivated and whether that guarantees a continuous embedding into a locally convex topological vector space.}

\textcolor{blue}{Generalize information geometry to the infinite-dimensional case---would require a locally convex topology to be able to define variations.}

\textcolor{blue}{Determine whether the ensemble spaces can be in general proven to be metrizable and characterize the connection between the metric and the entropy.}

\textcolor{blue}{Generalize classical mechanics and classical field theory.}

\textcolor{blue}{Find a suitable function space that can be used as a model for the case of classical field theories.}

The primary significance of the proposed research is that it will \textcolor{blue}{[has the potential to?] provide a common axiomatic foundation for \emph{all} physical theories.  Such an axiomatic foundation common to all physical theories will serve not only to better ground current theories and elucidate their relationships to one another, but also to constrain potential future physical theories, and perhaps point to assumptions or structures in current theories that hold promise for modification in order to develop new theories.}

\textcolor{blue}{[Rewrite above paragraph along these lines] We don't know where the mathematical structures in physics come from.  Therefore, when people try to generalize them, they do not know in which direction they can be generalized.  What we're doing is instead finding axioms from physical requirements---things the physics must at least give you.  The axiomatics are justified from the physics.  We're doing the due diligence to check that the axioms can be justified from the physics and they're independent of each other.  So when we're doing the generalization, the generalization is better constrained by the physics.}

Regarding the relationship of this work to the present state of knowledge in the field, while there exists other work attempting to reconstruct quantum mechanics from physical principles, for example in Refs.~\cite{hardy2001quantumaxioms,caticha2008,dakic2009,Chiribella2010,Masanes_2011}, we are not aware of any literature \textcolor{blue}{attempting to relate the geometric and entropic structures of quantum mechanics, much less in a general physical theory. One sentence about general approach(es) of those works?  There are people trying to reconstruct QM from physical premises, but these works are typically on finite dimensions and do not generalize to CM, and definitely don't generalize to classical or quantum field theories.}

@@

\noindent
\textbf{Assessment of intellectual merit:} \\
\textcolor{blue}{We will know if the proposed research program is successful if [proofs work!].  [Alternatively, if we conclude that these axioms are insufficient.]}
